### 2019-12-13 article.tex
some details about data preparation added, cnn architecture attached to the article

Proposed method can be briefly expressed as Algorithm \ref{alg:preprocessing}.

@@

>>>>

The proposed method can be briefly expressed as Algorithm \ref{alg:proposedMethod}. First of all, input data will be preprocessed using Algorithm \ref{alg:preprocessing}, which removes noises and non-informational data parts (such as the skull). In addition to that, each patient's scan will be normalized to a standard space that boosts the learning phase's efficiency. This step is followed by dividing each sample (containing $t$ 3D fMRI time-slices) to $t$ different images. For instance, in Parkinson's dataset, 30 samples consisted of 198 time-slices of \texttt{$39 \times 64 \times 64$} voxels will turn into $5940$ 3D images. We convert these data to TFRECORD format to improve performance. Furthermore, for each experiment, six participants ($20\%$ of all data) from both groups are randomly selected, and their $t$ time-slices are set aside for the test phase. On the other hand, the rest of the data (which are $24 \times 198$ labeled time-slices) will be shuffled and fed to our 3D deep Bayesian convolutional neural network. We use the first 158 time-slices as training samples while the remnants will be our validation portion of data correspondingly.

@@

Now we can start to train our model based on the proposed architecture which is illustrated in Figure \ref{fig:cnnArch}.

\begin{figure}
	\includegraphics[width=\linewidth]{images/cnnArch}
	\caption{proposed Bayesian 3D CNN architecture}
	\label{fig:cnnArch}
\end{figure}
